Software Ticket Quality

### 2017-10-31 proposal/mprop.tex
Work on paper on data quality in context

>>>>

\textbf{Data Quality in Context}\cite{strong1997data}:
\begin{itemize}
  \item \textbf{What were the goals?}

  \item \textbf{What was the method?}
    They performed a qualitative analysis, examining 42 data quality probjects 
    from 3 organizations. They collected data via inteviews of data procedures,
    custodians, customers and managers. The authors analysed each project using
    the data quality dimensions as content analysis codes. 
  \item \textbf{What did they learn?}
  \item \textbf{Relevance to our work}:
\end{itemize}
